Conferencia \textbf{SIGSOFT FSE}
\begin{itemize}
  \begin{small}
  \item Experience report: using RESOLVE/C++ for commercial software.\\
  Bruce W. Weide (Ohio State University), Joseph E. Hollingsworth (Indiana University Southeast), Lori Blankenship (Holly Software, Inc. Floyds Knobs).\\
  $0.25\%$ LANGUAGES, $0.25\%$ KNOWLEDGE ENGINEERING, $0.50\%$ FORMAL METHODS.
  \item Interpolation for data structures.\\
  Rupak Majumdar (University of California Los Angeles), Deepak Kapur (University of New Mexico), Calogero G. Zarba (Saarland University).\\
  $0.50\%$ LANGUAGES, $0.50\%$ FORMAL METHODS.
  \item An empirical study of the effect of time constraints on the cost-benefits of regression testing.\\
  Gregg Rothermel (University of Nebraska Lincoln), Hyunsook Do (North Dakota State University), Siavash Mirarab (University of Waterloo), Ladan Tahvildari (University of Waterloo).\\
  $0.33\%$ TESTING, $0.67\%$ RELIABILITY.
  \item Differential symbolic execution.\\
  Sebastian G. Elbaum (University of Nebraska Lincoln), Matthew B. Dwyer (University of Nebraska Lincoln), Corina S. Pasareanu (National Aeronautics and Space, Administration, United States), Suzette Person (National Aeronautics and Space Administration, United States).\\
  $0.25\%$ TESTING, $0.25\%$ ARCHITECTURES, $0.50\%$ FORMAL METHODS.
  \end{small}
\end{itemize}

Conferencia \textbf{ASE}
\begin{itemize}
  \begin{small}
  \item The power of software.\\
  Alfonso Fuggetta (Politecnico di Milano). \\
  $0.75\%$ LANGUAGES, $0.25\%$ SOFTWARE QUALITY.
  \item Bogor/Kiasan: A k-bounded Symbolic Execution for Checking Strong Heap Properties of Open Systems.\\
  Xianghua Deng (Pennsylvania State University), Jooyong Lee (Korea University), Robby (Kansas State University).\\
  $0.30\%$ TESTING, $0.30\%$ LANGUAGES, $0.40\%$ FORMAL METHODS.
  \item A dynamic birthmark for java.\\
  Christian Lindig (Harvard University), David Schuler (Saarland University), Valentin Dallmeier (Saarland University).\\
  $0.67\%$ TESTING, $0.33\%$ SECURITY.
  \item MTSA: The Modal Transition System Analyser.\\
  Marsha Chechik (University of Toronto), Sebastián Uchitel (Universidad de Buenos Aires), Nicolás D'Ippolito (Universidad de Buenos Aires), Dario Fischbein (Imperial College London).\\
  $0.625\%$ MODELS, $0.375\%$ FORMAL METHODS.
  \end{small}
\end{itemize}

Conferencia \textbf{ICSE}
\begin{itemize}
  \begin{small}
  \item Modeling ontologies as executable domain specific languages.\\
  Dragan Djuric (NULL), Jelena Jovanovic (University of Belgrade), Ramo Sendelj (Mediterranean University Montenegro), Vladan Devedzic (University of Belgrade).\\
  $0.50\%$ TESTING, $0.50\%$ DISTRIBUTED SYSTEMS.
  \item The Property Vector Specification of a Multiset Iterator.\\
  David Alex Lamb (Liverpool John Moores University), Trevor W. Pearce (Carleton University).\\
  $0.67\%$ LANGUAGES, $0.25\%$ FORMAL METHODS.
  \item Modeling behavioral design patterns of concurrent objects.\\
  Hassan Gomaa (George Mason University), Robert G. Pettit IV (George Mason University).\\
  $0.50\%$ LANGUAGES, $0.50\%$ DISTRIBUTED SYSTEMS.
  \item How we refactor, and how we know it.\\
  Andrew P. Black (Portland State University), Chris Parnin (Georgia Institute of Technology), Emerson R. Murphy-Hill (North Carolina State University).\\
  $0.33\%$ LANGUAGES, $0.67\%$ PROGRAM COMPREHENSION.
  \end{small}
\end{itemize}

Conferencia \textbf{ACM Trans. Softw. Eng. Methodol.}
\begin{itemize}
  \begin{small}
  \item A Time-Sensitive Object Model for Real-Time Systems.\\
  H. Rebecca Callison (University of Washington).\\
  $0.33\%$ REAL TIME SYSTEMS, $0.33\%$ LANGUAGES, $0.34\%$ FORMAL METHODS.
  \item Distributed Real-Time System Specification and Verification in APTL.\\
  Aloysius K. Mok (University of Texas Austin), Farn Wang (National Taiwan University), E. Allen Emerson (University of Texas Austin).\\
  $0.33\%$ LANGUAGES, $0.33\%$ DISTRIBUTED SYSTEMS, $0.34\%$ FORMAL METHODS.
  \item The role of outcome feedback in improving the uncertainty assessment of software development effort estimates.\\
  Magne Jørgensen (Simula Research Laboratory), Tanja M. Gruschke (Simula Research Laboratory).\\
  $0.50\%$ MAINTENANCE, $0.50\%$ INFORMATION SYSTMS.
  \item An inheritance-based technique for building simulation proofs incrementally.\\
  Nancy A. Lynch (Massachusetts Institute of Technology), Idit Keidar (Technion Israel Institute of Technology), Roger Khazan (Massachusetts Institute of Technology), Alexander A. Shvartsman (University of Connecticut).\\
  $0.50\%$ LANGUAGES, $0.50\%$ DISTRIBUTED SYSTEMS.
  \end{small}
\end{itemize}

Conferencia \textbf{IEEE Trans. Software Eng.}
\begin{itemize}
  \begin{small}
  \item An Empirical Study of Test Case Filtering Techniques Based on Exercising Information Flows.\\
  Wes Masri (American University of Beirut), David Leon (Case Western Reserve University), Andy Podgurski (Case Western Reserve University).\\
  $0.26\%$ TESTING, $0.14\%$ LANGUAGES, $0.60\%$ RELIABILITY.
  \item Synthesis of Decision-Free Concurrent Systems for Prescribed Resources and Performance.\\
  Tadao Murata (University of Illinois Chicago).\\
  $0.25\%$ DISTRIBUTED SYSTEMS, $0.75\%$ FORMAL METHODS.
  \item Independent Recovery in Large-Scale Distributed Systems.\\
  Peter Triantafillou (University of Patras).\\
  $0.33\%$ DATABASE, $0.33\%$ DISTRIBUTED SYSTEMS, $0.34\%$ KNOWLEDGE ENGINEERING.
  \item On Parallel Processing Systems: Amdahl's Law Generalized and Some Results on Optimal Design.\\
  Leonard Kleinrock (University of California Los Angeles), Jau-Hsiung Huang (National Taiwan University).\\
  $0.67\%$ DISTRIBUTED SYSTEMS, $0.33\%$ RELIABILITY.
  \end{small}
\end{itemize}