\begin{center}
\begin{longtable}{|p{0.08\textwidth}p{0.3\textwidth}p{0.2\textwidth}p{0.3\textwidth}|}
    \hline
    Bundle & Title & Venue & Authors \\
    \hline
\rowcolor{black!20}    1	& Learning Communicating Automata from MSCs.& IEEE Trans. Software 
Eng.& Benedikt Bollig, Martin Leucker, Carsten Kern, Joost-Pieter Katoen \\
	& HOTTest: A model-based test design technique for enhanced testing of domain-specific 
applications.& ACM Trans. Softw. Eng. Methodol.& Carol Smidts, Avik Sinha \\
\rowcolor{black!20}	& A lightweight approach for program analysis and debugging.& ICSE& M. G. 
Rakesh \\
	& DESERT: a decentralized monitoring tool generator.& ASE& Paola Inverardi, Leonardo 
Mostarda \\
\rowcolor{black!20}	& PENELOPE: weaving threads to expose atomicity violations.& SIGSOFT FSE& 
Francesco Sorrentino 0002, Azadeh Farzan, P. Madhusudan \\
    2	& Performance of Storage Management in an Implementation of SNOBOL4.& IEEE Trans. Software 
Eng.& Ralph E. Griswold, David R. Hanson, G. David Ripley \\
\rowcolor{black!20}	& Model checking the Java metalocking algorithm.& ACM Trans. Softw. Eng. 
Methodol.& Scott A. Smolka, Samik Basu \\
	& Software design sketching with calico.& ASE& André van der Hoek, Nicolas Mangano, Mitch 
Dempsey, Alex Baker, Emily Oh Navarro \\
\rowcolor{black!20}	& Towards Safe Distributed Application Development.& ICSE& Rachid 
Guerraoui, 
Christian Heide Damm, Patrick Th. Eugster \\
	& Checking Relational Specifications With Binary Decision Diagrams.& SIGSOFT FSE& Daniel 
Jackson, Craig Damon, Somesh Jha \\
\rowcolor{black!20}    3	& GUI Interaction Testing: Incorporating Event Context.& IEEE 
Trans. 
Software Eng.& Myra B. Cohen, Atif M. Memon, Xun Yuan \\
	& Test conditions for fault classes in Boolean specifications.& ACM Trans. Softw. Eng. 
Methodol.& Jonathan P. Bowen, Kalpesh Kapoor \\
\rowcolor{black!20}	& Test suite reduction and prioritization with call trees.& ASE& Mary Lou 
Soffa, Gregory M. Kapfhammer, Joshua Geiger, Adam M. Smith \\
	& Experimental program analysis: a new paradigm for program analysis.& ICSE& Joseph R. 
Ruthruff \\
\rowcolor{black!20}	& Automated identification of parameter mismatches in web applications.& 
SIGSOFT FSE& Alessandro Orso, William G. J. Halfond \\
    4	& Interface Grammars for Modular Software Model Checking.& IEEE Trans. Software Eng.& 
Tevfik 
Bultan, Graham Hughes \\
\rowcolor{black!20}	& Amoeba: A methodology for modeling and evolving cross-organizational 
business processes.& ACM Trans. Softw. Eng. Methodol.& Nirmit Desai, Amit K. Chopra, Munindar P. 
Singh \\
	& Japanese Workshop on Leveraging Web2.0 Technologies in Software Development Environments 
(WebSDE).& ASE& Makoto Matsushita, Katsuhisa Maruyama, Shinichiro Yamamoto \\
\rowcolor{black!20}	& Architectures and Technologies for Enterprise Application Integration.& 
ICSE& Ian Gorton, Anna Liu \\
	& Local analysis of atomicity sphere for B2B collaboration.& SIGSOFT FSE& Chang Xu, 
Chunyang Ye, W. K. Chan, S. C. Cheung \\
\rowcolor{black!20}    5	& Comments on Program Slicing.& IEEE Trans. Software Eng.& Hareton 
K. N. Leung, Hassan K. Reghbati \\
	& Software reuse for scientific computing through program generation.& ACM Trans. Softw. 
Eng. Methodol.& Martin Erwig, Zhe Fu \\
\rowcolor{black!20}	& Automatic Generation of Content Management Systems from EER-Based 
Specifications.& ASE& Sebastiano Vigna \\
	& Enhancing Software Testing by Judicious Use of Code Coverage Information.& ICSE& Roland 
Weber, Stefan Berner, Rudolf K. Keller \\
\rowcolor{black!20}	& Automatically locating framework extension examples.& SIGSOFT FSE& Harold 
Ossher, Barthélémy Dagenais \\
    6	& On the Optimal Total Processing Time Using Checkpoints.& IEEE Trans. Software Eng.& Zohel 
Khalil, Boyan Dimitrov, Nikolay Kolev, Peter Petrov \\
\rowcolor{black!20}	& Equivalence analysis and its application in improving the efficiency of 
program slicing.& ACM Trans. Softw. Eng. Methodol.& Mary Jean Harrold, Donglin Liang \\
	& Synthesizing client load models for performance engineering via web crawling.& ASE& John 
C. Grundy, John G. Hosking, Yuhong Cai \\
\rowcolor{black!20}	& Spontaneous software: a Web-based, object computing paradigm.& ICSE& 
Glêdson Elias da Silveira \\
	& Containment units: a hierarchically composable architecture for adaptive systems.& 
SIGSOFT FSE& Leon J. Osterweil, Barbara Staudt Lerner, Alexander E. Wise, Jamieson M. Cobleigh \\
\rowcolor{black!20}    7	& Experiences Using Lightweight Formal Methods for Requirements 
Modeling.& IEEE Trans. Software Eng.& David Hamilton, Steve M. Easterbrook, Robyn R. Lutz, John 
Kelly, Richard Covington, Yoko Ampo \\
	& Metamodel-based model conformance and multiview consistency checking.& ACM Trans. Softw. 
Eng. Methodol.& Jonathan S. Ostroff, Richard F. Paige, Phillip J. Brooke \\
\rowcolor{black!20}	& Automating Software Traceability in Very Small Companies: A Case Study 
and 
Lessons Learne.& ASE& Paul Grünbacher, Christian Neumuller \\
	& Metrics for model driven requirements development.& ICSE& Brian Berenbach, Gail Borotto \\
\rowcolor{black!20}	& Composable semantics for model-based notations.& SIGSOFT FSE& Jianwei 
Niu, 
Joanne M. Atlee, Nancy A. Day \\
    8	& Rapid Transaction-Undo Recovery Using Twin-Page Storage Management.& IEEE Trans. Software 
Eng.& Kun-Lung Wu, W. Kent Fuchs \\
\rowcolor{black!20}	& The Use of Description Logics in KBSE Systems: Experience Report.& ICSE& 
Premkumar T. Devanbu, Mark A. Jones \\
	& Using assertions to help end-user programmers create dependable web macros.& SIGSOFT FSE& 
Gregg Rothermel, Sebastian G. Elbaum, Lorin Hochstein, Christopher Scaffidi, Kathryn T. Stolee, 
Andhy Koesnandar \\
\rowcolor{black!20}	& Declarative Specification of Software Architectures.& ASE& John Penix, 
Klaus Havelund, Perry Alexander \\
    9	& On Homogeneity and On-Line=Off-Line Behavior in M/G/1 Queueing Systems.& IEEE Trans. 
Software Eng.& Raymond M. Bryant \\
\rowcolor{black!20}	& Tools and experiments supporting a testing-based theory of component 
composition.& ACM Trans. Softw. Eng. Methodol.& Dick Hamlet \\
	& RCAT: A Performance Analysis Tool.& ASE& Zakarya Alzamil \\
\rowcolor{black!20}	& An Introduction to the Programmer's Workbench.& ICSE& John R. Mashey, Ted 
A. Dolotta \\
    10	& Analogy-X: Providing Statistical Inference to Analogy-Based Software Cost Estimation.& 
IEEE Trans. Software Eng.& D. Ross Jeffery, Jacky Keung, Barbara A. Kitchenham \\
\rowcolor{black!20}	& An empirical investigation of software reuse benefits in a large telecom 
product.& ACM Trans. Softw. Eng. Methodol.& Reidar Conradi, Parastoo Mohagheghi \\
	& Fraunhofer: the German model for applied research and technology transfer.& ICSE& H. 
Dieter Rombach \\
\rowcolor{black!20}	& An Empirical Study of the Evolution of a Software System.& ASE& Rachel 
Harrison, Brian Warboys, R. Mark Greenwood, Peter Henderson \\
    \hline
    \caption {$\gamma$ $=$ $0.1$}
\end{longtable}
\end{center}