\begin{center}
\begin{longtable}{|p{0.1\textwidth}p{0.3\textwidth}p{0.2\textwidth}p{0.3\textwidth}|}
    \hline
    Bundle & Title & Venue & Authors \\
    \hline
    \rowcolor{black!20} 1 (100 \% Formal Methods) & Learning Communicating Automata from MSCs.& 
IEEE Trans. 
Software Eng.& Benedikt Bollig, Martin Leucker, Carsten Kern, Joost-Pieter Katoen \\
 & HOTTest: A model-based test design technique for enhanced testing of domain-specific 
applications.& ACM Trans. Softw. Eng. Methodol.& Carol Smidts, Avik Sinha \\
\rowcolor{black!20} & A lightweight approach for program analysis and debugging.& ICSE& M. G. Rakesh 
\\
 & DESERT: a decentralized monitoring tool generator.& ASE& Paola Inverardi, Leonardo Mostarda \\
\rowcolor{black!20} & PENELOPE: weaving threads to expose atomicity violations.& SIGSOFT FSE& 
Francesco Sorrentino 0002, Azadeh Farzan, P. Madhusudan \\
2 (100 \% Languages) & Performance of Storage Management in an Implementation of SNOBOL4.& IEEE 
Trans. 
Software Eng.& Ralph E. Griswold, David R. Hanson, G. David Ripley \\
\rowcolor{black!20} & Model checking the Java metalocking algorithm.& ACM Trans. Softw. Eng. 
Methodol.& Scott A.Smolka, Samik Basu \\
 & Software design sketching with calico.& ASE& André van der Hoek, Nicolas Mangano, Mitch Dempsey, 
Alex Baker, Emily Oh Navarro \\
\rowcolor{black!20} & Towards Safe Distributed Application Development.& ICSE& Rachid Guerraoui, 
Christian Heide Damm, Patrick Th. Eugster \\
 & Checking Relational Specifications With Binary Decision Diagrams.& SIGSOFT FSE& Daniel Jackson, 
Craig Damon, Somesh Jha \\
\rowcolor{black!20} 3 (100 \% Testing) & GUI Interaction Testing: Incorporating Event Context.& 
IEEE 
Trans. Software Eng.& Myra B. Cohen, Atif M. Memon, Xun Yuan \\
 & Test conditions for fault classes in Boolean specifications.& ACM Trans. Softw. Eng. Methodol.& 
Jonathan P. Bowen, Kalpesh Kapoor \\
\rowcolor{black!20} & Test suite reduction and prioritization with call trees.& ASE& Mary Lou Soffa, 
Gregory M. Kapfhammer, Joshua Geiger, Adam M. Smith \\
 & Experimental program analysis: a new paradigm for program analysis.& ICSE& Joseph R. Ruthruff \\
\rowcolor{black!20} & Automated identification of parameter mismatches in web applications.& SIGSOFT 
FSE& Alessandro Orso, William G. J. Halfond \\
4 (100 \% Services) & Interface Grammars for Modular Software Model Checking.& IEEE Trans. Software 
Eng.& 
Tevfik Bultan, Graham Hughes \\
\rowcolor{black!20} & Amoeba: A methodology for modeling and evolving cross-organizational business 
processes.& ACM Trans. Softw. Eng. Methodol.& Nirmit Desai, Amit K. Chopra, Munindar P. Singh \\
 & Japanese Workshop on Leveraging Web2.0 Technologies in Software Development Environments 
(WebSDE).& ASE& Makoto Matsushita, Katsuhisa Maruyama, Shinichiro Yamamoto \\
\rowcolor{black!20} & Architectures and Technologies for Enterprise Application Integration.& ICSE& 
Ian Gorton, Anna Liu \\
 & Local analysis of atomicity sphere for B2B collaboration.& SIGSOFT FSE& Chang Xu, Chunyang Ye, W. 
K. Chan, S. C. Cheung \\
\rowcolor{black!20} 5 (100 \% Maintenance) & Comments on Program Slicing.& IEEE Trans. Software 
Eng.& 
Hareton K. N. Leung, Hassan K. Reghbati \\
 & Software reuse for scientific computing through program generation.& ACM Trans. Softw. Eng. 
Methodol.& Martin Erwig, Zhe Fu \\
\rowcolor{black!20} & Automatic Generation of Content Management Systems from EER-Based 
Specifications.& ASE& Sebastiano Vigna \\
 & Enhancing Software Testing by Judicious Use of Code Coverage Information.& ICSE& Roland Weber, 
Stefan Berner, Rudolf K. Keller \\
\rowcolor{black!20} & Automatically locating framework extension examples.& SIGSOFT FSE& Harold 
Ossher, Barthélémy Dagenais \\
6 (100 \% Languages) & Validating a Demonstration Tool for Graphics-Assisted Debugging of Ada 
Concurrent 
Programs.& IEEE Trans. Software Eng.& Michael B. Feldman, Melinda L. Moran \\
\rowcolor{black!20} & Unifying aspect- and object-oriented design.& ACM Trans. Softw. Eng. 
Methodol.& Kevin J.Sullivan, Hridesh Rajan \\
 & Eliminating products to test in a software product line.& ASE& Don S. Batory, Sarfraz Khurshid, 
Chang Hwan Peter Kim \\
\rowcolor{black!20} & Requirements, domain and specifications: a viewpoint-based approach to 
requirements engineering.& ICSE& Andrés Silva \\
 & Effective blame for information-flow violations.& SIGSOFT FSE& Somesh Jha, Dave King 0002, Trent 
Jaeger, Sanjit A. Seshia \\
\rowcolor{black!20} 7 (95 \% Formal Methods, 5 \% Others) & An Interval Logic for Real-Time System 
Specification.& IEEE 
Trans. Software Eng.& Paolo Nesi, Riccardo Mattolini \\
 & Reasoning about static and dynamic properties in alloy: A purely relational approach.& ACM Trans. 
Softw. Eng. Methodol.& Nazareno Aguirre, T. S. E. Maibaum, Gabriel A. Baum, Marcelo F. Frias, Carlos 
López Pombo \\
\rowcolor{black!20} & Automated Software Engineering Using Concurrent Class Machines.& ASE& Scott A. 
Smolka, Yanhong A. Liu, Jingyu Yan, Scott D. Stoller, Radu Grosu \\
 & HighSpec: a tool for building and checking OZTA models.& ICSE& Shengchao Qin, Jin Song Dong, Ping 
Hao, Xian Zhang \\
\rowcolor{black!20} & COM revisited: tool-assisted modelling of an architectural framework.& SIGSOFT 
FSE& Daniel Jackson, Kevin J. Sullivan \\
8 (94 \% Testing, 6 \% Others) & Carving and Replaying Differential Unit Test Cases from System 
Test Cases.& IEEE 
Trans. Software Eng.& Sebastian G. Elbaum, Matthew B. Dwyer, Matthew Jorde, Hui Nee Chin \\
\rowcolor{black!20} & Empirical evaluation of a nesting testability transformation for evolutionary 
testing.& ACM Trans. Softw. Eng. Methodol.& David Binkley, Mark Harman, Phil McMinn \\
 & Unit testing concurrent software.& ASE& William Pugh, Nathaniel Ayewah \\
\rowcolor{black!20} & Practical change impact analysis based on static program slicing for 
industrial software systems.& ICSE& Mithun Acharya, Brian Robinson \\
 & Efficient incremental algorithms for dynamic detection of likely invariants.& SIGSOFT FSE& 
Michael D. Ernst, Jeff H. Perkins \\
\rowcolor{black!20} 9 (95 \% Distributed System, 5 \% Program Analysis) & On the Optimal Total 
Processing Time Using 
Checkpoints.& IEEE Trans. Software Eng.& Zohel Khalil, Boyan Dimitrov, Nikolay Kolev, Peter Petrov 
\\
 & Equivalence analysis and its application in improving the efficiency of program slicing.& ACM 
Trans. Softw. Eng. Methodol.& Mary Jean Harrold, Donglin Liang \\
\rowcolor{black!20} & Synthesizing client load models for performance engineering via web crawling.& 
ASE& John C. Grundy, John G. Hosking, Yuhong Cai \\
 & Spontaneous software: a Web-based, object computing paradigm.& ICSE& Glêdson Elias da Silveira \\
\rowcolor{black!20} & Containment units: a hierarchically composable architecture for adaptive 
systems.& SIGSOFT FSE& Leon J. Osterweil, Barbara Staudt Lerner, Alexander E. Wise, Jamieson M. 
Cobleigh \\
10 (100 \% Languages) & An Application of a Method for Analysis of Cyclic Programs.& IEEE Trans. 
Software 
Eng.& Nissim Francez \\
\rowcolor{black!20} & Task Dependence and Termination in Ada.& ACM Trans. Softw. Eng. Methodol.& 
Laura K. Dillon \\
 & Static Typing for Ruby on Rails.& ASE& Jeffrey S. Foster, Avik Chaudhuri, Jong-hoon (David) An \\
\rowcolor{black!20} & Mining Security-Sensitive Operations in Legacy Code Using Concept Analysis.& 
ICSE& Somesh Jha, Dave King 0002, Trent Jaeger, Vinod Ganapathy \\
 & Scalable SMT-based verification of GPU kernel functions.& SIGSOFT FSE& Ganesh Gopalakrishnan, 
Guodong Li \\
    \hline
    \caption{$\gamma$ $=$ $0.9$}
\end{longtable}
\end{center}