\begin{center}
\begin{longtable}{|p{0.2\textwidth}p{0.2\textwidth}p{0.2\textwidth}p{0.3\textwidth}|}
    \hline
    Bundle & Title & Venue & Authors \\
    \hline
\rowcolor{black!20} 1 (53 \% Program Comprehension, 10 \% Reliability, 8 \% Distributed Systems, 6 
\% Architectures, 4 \% Information Systems, 19 \% Ohters) & Formal interpreters for diagram 
notations.& ACM Trans. Softw. Eng. 
Methodol.& Mauro Pezzè, Luciano Baresi \\
 & Software systems as cities: a controlled experiment.& ICSE& Michele Lanza, Romain Robbes, Richard 
Wettel \\
\rowcolor{black!20} & Marple: a demand-driven path-sensitive buffer overflow detector.& SIGSOFT FSE& 
Mary Lou Soffa, Wei Le \\
 & An Economic Model to Estimate Software Rewriting and Replacement Times.& IEEE Trans. Software 
Eng.& Teck Hua Ho, Taizan Chan, Siu Leung Chung \\
\rowcolor{black!20} & A DSL Approach to Improve Productivity and Safety in Device Drivers 
Development.& ASE& Gilles Muller, Laurent Réveillère, Charles Consel, Renaud Marlet, Fabrice 
Mérillon \\
2 (50 \& Methodologies, 20 \% Metrics, 10 \% Real Time Systems, 10 \% Human Computer Interaction, 4 
\% Requirements, 6 \% Ohters) & The Case for Electric Design of Real-Time Software.& IEEE Trans. 
Software Eng.& Bo Sanden \\
\rowcolor{black!20} & Temporal abstract classes and virtual temporal specifications for real-time 
systems.& ACM Trans. Softw. Eng. Methodol.& Alexander P. Pons \\
 & Clone-Aware Configuration Management.& ASE& Tien N. Nguyen, Jafar M. 
Al-Kofahi, Hoan Anh Nguyen, Nam H. Pham, Tung Thanh Nguyen \\
\rowcolor{black!20} & Experience applying the SPIN model checker to an industrial telecommunications 
system.& ICSE& T. C. Nicholas Graham, Jürgen Dingel, Barry Long \\
 & Integrating Status and Event Phenomena in Formal Specifications of Interactive Systems.& SIGSOFT 
FSE& Gregory D. Abowd, Alan J. Dix \\
\rowcolor{black!20} 3 (40 \% Database, 20 \% Knowledge Engineering, 20 \% Performance, 4 \% 
Concurrency, 4 \% Software Quality, 88 \% Ohters) & Xstream: A Middleware for Streaming XML 
Contents over Wireless Environments.& IEEE Trans. Software Eng.& Alvin T. S. Chan, Hong Va Leong, 
Eugene Y. C. Wong \\
 & Tools and experiments supporting a testing-based theory of component composition.& ACM Trans. 
Softw. Eng. Methodol.& Dick Hamlet \\
\rowcolor{black!20} & Checking Subsystem Safety Properties in Compositional Reachability Analysis.& 
ICSE& Jeff Kramer, Shing-Chi Cheung \\
 & Using assertions to help end-user programmers create dependable web macros.& SIGSOFT FSE& Gregg 
Rothermel, Sebastian G. Elbaum, Lorin Hochstein, Christopher Scaffidi, Kathryn T. Stolee, Andhy 
Koesnandar \\
\rowcolor{black!20} & Semantic Links and Co-Evolution in Object-Oriented Software Development.& ASE& 
Ragnhild Van Der Straeten \\
4 (40 \% Testing, 20 \% Education, 20 \% Program Analysis, 6. \% Empirical Software Engineering, 14 
\% Ohters) & A Theoretical and Empirical Study of Search-Based Testing: Local, Global, and Hybrid 
Search.& IEEE Trans. Software Eng.& Mark Harman, Phil McMinn \\
\rowcolor{black!20} & Software Trustability Analysis.& ACM Trans. Softw. Eng. Methodol.& William E. 
Howden, Yudong Huang \\
 & SEREBRO: facilitating student project team collaboration.& ICSE& Rose F. Gamble, Noah Jorgenson, 
Matthew L. Hale \\
\rowcolor{black!20} & Searching for points-to analysis.& SIGSOFT FSE& Glenn Bruns, Satish Chandra \\
 & Precise Specification and Automatic Application of Design Patterns.& ASE& Amiram Yehudai, Joseph 
Gil, Amnon H. Eden \\
\rowcolor{black!20} 5 (40 \% Adaptive Systems, 20 \% Requirements, 20 \% Performance, 7 \% Software 
Quality, 13 \% Ohters) & Simplifying and Isolating Failure-Inducing Input.& IEEE Trans. Software 
Eng.& Andreas Zeller, Ralf Hildebrandt \\
 & Tools and experiments supporting a testing-based theory of component composition.& ACM Trans. 
Softw. Eng. Methodol.& Dick Hamlet \\
\rowcolor{black!20} & Formalization and Application of a Unifying Model for Name Management.& 
SIGSOFT FSE& Jack C. Wileden, Alan Kaplan \\
 & NAVCo: Negotiation-based Adaptive View Coordination.& ASE& Prasanta K. Bose, Mark G. Matthews \\
\rowcolor{black!20} & Software Architecture Based on Communicating Residential Environments.& ICSE& 
Erik Sandewall, Claes Strömberg, Henrik Sörensen \\
6 (20 \% Services, 20 \% Program Analysis, 20 \% Operating Systems, 20 \% Embedded, 6 \% Education, 
5 \% Reliability, 9 \% Ohters) & Cleanroom Software Development: An Empirical Evaluation.& IEEE 
Trans. Software Eng.& Victor R. Basili, Richard W. Selby, Terry Baker \\
\rowcolor{black!20} & Amoeba: A methodology for modeling and evolving cross-organizational business 
processes.& ACM Trans. Softw. Eng. Methodol.& Nirmit Desai, Amit K. Chopra, Munindar P. Singh \\
 & Validating Automotive Control Software Using Instrumentation-Based Verification.& ASE& Rance 
Cleaveland, Arnab Ray, Chris Martin, Charles P. Shelton, Iris Morschhaeuser, Christopher Ackermann 
\\
\rowcolor{black!20} & Searching for points-to analysis.& SIGSOFT FSE& Glenn Bruns, Satish Chandra \\
 & On the Influence of Scale in a Distributed System.& ICSE& Mahadev Satyanarayanan \\
\rowcolor{black!20} 7 (40 \% Distributed Systems, 40 \% Reverse Engineering, 4 \% Program 
Comprehension, 4 \% Database, 12 \% Ohters) & Formal Grammar and Human Factors Design of an 
Interactive Graphics System.& IEEE Trans. Software Eng.& Phyllis Reisner \\
 & Double Iterative Framework for Flow-Sensitive Interprocedural Data Flow Analysis.& ACM Trans. 
Softw. Eng. Methodol.& István Forgács \\
\rowcolor{black!20} & Visualizing clone detection results.& ASE& Jeff Gray, Robert Tairas, Ira D. 
Baxter \\
 & Spontaneous software: a Web-based, object computing paradigm.& ICSE& Glêdson Elias da Silveira \\
\rowcolor{black!20} & Basset: a tool for systematic testing of actor programs.& SIGSOFT FSE& Gul 
Agha, Darko Marinov, Steven Lauterburg, Rajesh K. Karmani \\
8 (20 \% Information Systems, 13 \% Languages, 11 \% Artificial Intelligence, 7 \% Formal Methods, 7 
\% Visualization, 6 \% Algorithm, 6 \% Metrics, 30 \% Ohters) & Using Annotations to Make Recursion 
Equations Behave.& IEEE Trans. Software Eng.& Jerald Schwarz \\
\rowcolor{black!20} & Hybrid Slicing: Integrating Dynamic Information with Static Analysis.& ACM 
Trans. Softw. Eng. Methodol.& Mary Lou Soffa, Rajiv Gupta, John Howard \\
 & Software Cost Estimation using Fuzzy Decision Trees.& ASE& Andreas S. Andreou, Efi 
Papatheocharous \\
\rowcolor{black!20} & Making Resource Decisions for Software Projects.& ICSE& Norman E. Fenton, 
Martin Neil, Patrick Cates, Simon Forey, Manesh Tailor, William Marsh \\
 & Implicit context: easing software evolution and reuse.& SIGSOFT FSE& Robert J. Walker, Gail C. 
Murphy \\
\rowcolor{black!20} 9 (40 \% Human Computer Interaction, 20 \% Formal Methods, 13 \% Metrics, 10 \% 
Security, 6 \% Distributed Systems, 11 \% Ohters) & A Machine Description Facility for Compiler 
Testing.& IEEE Trans. Software Eng.& Hanan Samet \\
 & Functional size measurement revisited.& ACM Trans. Softw. Eng. Methodol.& Onur Demirörs, Çigdem 
Gencel \\
\rowcolor{black!20} & Code Completion from Abbreviated Input.& ASE& Robert C. Miller, Sangmok Han, 
David R. Wallace \\
 & Deriving input syntactic structure from execution.& SIGSOFT FSE& Zhiqiang Lin, Xiangyu Zhang \\
\rowcolor{black!20} & Empowering Software Engineers in Human-Centered Design.& ICSE& Alina 
Andreevskaia, Ahmed Seffah \\
10 (20 \% Program Analysis, 20 \% Education, 20 \% Synthesis, 20 \% Performance, 7 \% Reliability, 
13 \% Ohters) & The Unix System and Software Reusability.& IEEE Trans. Software Eng.& Brian W. 
Kernighan \\
\rowcolor{black!20} & Tools and experiments supporting a testing-based theory of component 
composition.& ACM Trans. Softw. Eng. Methodol.& Dick Hamlet \\
 & SEREBRO: facilitating student project team collaboration.& ICSE& Rose F. Gamble, Noah Jorgenson, 
Matthew L. Hale \\
\rowcolor{black!20} & Searching for points-to analysis.& SIGSOFT FSE& Glenn Bruns, Satish Chandra \\
 & COMPASS: Tool-Supported Adaptation of Interactions.& ASE& Dirk Heuzeroth \\
    \hline
    \caption {$\gamma$ $=$ $0.1$}
\end{longtable}
\end{center}